Adaptive broadcast tree for multicores

### 2013-06-09 paper.tex
New visualization applied to all combinations of machines and topologies except for rings
Migration to event based send events (rather than sending them sequentially). This is a first step towards building the topology iteratively and adaptively during evaluation. Visualization seems to be broken now, though

% tikz stuff
\usepackage{tikz}
\usepackage{pgfplots}
% configuration
\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes}
\pgfplotsset{width=.9\linewidth}

@@

Next, we evaluate ring topologies. Rings have the advantage that the
implicitly acknowledge messages once they arrive back to the
sender. This is beneficial for some algorithms such as quorums, where
nodes report back to the sender. This, however, only works if forwarding
along the ring is only done after all local nodes acknowledge a
message.

@@

To add more parallelism, we add a second ring, which we send the
message on in parallel. The overlay ring network is visualized in
Figure~\ref{fig:gruyere_ring}. Node that the link from node 20 to 8 is
a two hop link and, thus, has a cost of 20 instead of the usual 10.

>>>>

% tikz stuff
\usepackage{tikz}
\usepackage{pgfplots}
% configuration
\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes,fit,backgrounds}
\pgfplotsset{width=.9\linewidth}

@@

Next, we evaluate ring topologies. Rings experience a certain level of
redundancy. The sending node receives the node back on the ring. This
is unnecessary for applications with uni-directional traffic executed
on reliable communication channels

For applications that require some form of feedback (as well as
unreliable channels, which we do not consider at this point), rings
have the advantage that they can piggy-back some information that will
eventually arrive back on the sender. This is beneficial for some
algorithms such as quorums, where nodes report the result of the
quorum back to the sender.

@@

To add more parallelism, we add a second ring, which we send the
message on in parallel. Acknowledgments, however, only work if
forwarding along the ring is only done after all local nodes (as in
nodes from the outer rings) acknowledge a message. In
Figure~\ref{fig:gruyere_ring}, we visualize an example of two
intertwined ring topologies. Node that the link from node 20 to 8 is a
two hop link and, thus, has a cost of 20 instead of the usual 10.
